Economic Evaluation of Geographically Weighted Regression Analysis for Site-specific Nitrogen Management

### 2023-04-22 Writing/manuscript_gwr.rmd
minor edit

Precision agriculture (also known as site-specific farming, or variable-rate technology) is a management strategy that adjusts farm management decisions according to the spatial and temporal variability of soil and crop conditions within a field. Over the past few decades, numerous technological innovations have been made in collecting detailed field information (e.g., yield mapping, soil sampling, remote sensing, etc.) and developing site-specific management recommendations based on the information. However, the long-standing question of whether the economic benefit of precision agriculture can offset the technology and information costs [@lowenberg1996revolution; @weiss1996precision] remains difficult to answer, particularly in the context of large-scale production systems [@mcfadden2022information].

>>>>

Precision agriculture is a management strategy that adjusts farm management decisions according to the spatial and temporal variability of soil and crop conditions within a field. Over the past few decades, numerous technological innovations have been made in collecting detailed field information (e.g., yield mapping, soil sampling, remote sensing, etc.) and developing site-specific management recommendations based on the information. However, the long-standing question of whether the economic benefit of precision agriculture can offset the technology and information costs [@lowenberg1996revolution; @weiss1996precision] remains difficult to answer, particularly in the context of large-scale production systems [@mcfadden2022information].
